Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-17 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Reviewing English from abstract and introduction

\begin{abstract}
Volunteer computing is used routinely in science and industry, but it
still has a long way to go if it is going to become a mainstream technology in
the same way the cloud technologies in general have. The lack of general
purpose and open source tools
with analytics built in could be one of the reasons why this is so, as
well as the lack of proofs of concept. That is why in this paper we
present {\sf NodIO}, a framework used to create client-server architectures for distributed
evolutionary algorithms, written entirely in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser.  The architecture, along with some initial results on the
expected performance and scaling
behavior is presented. We also use the algorithm data to
find out what kind of patterns the user behavior follow and try to fit
them to some statistical distribution.
\end{abstract}

@@

There is, then, space for systems that do not make any of these
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. {\sf NodIO} is first a two tier client/server 
application, in which clients can run in a browser. 
Therefore, they can embedded any web-enabled device, including many over which 
the developers have no control.

Some time ago, our group faced the problem of diminishing funds for
buying new hardware. This was aggravated by the increasing maintenance costs and
extended downtime resulting from the continuous failures of existing
clusters.
Considering this, we leveraged our experience in the design of web
applications, including JavaScript, since their inception and other
volunteer and
unconventional distributed evolutionary computing systems, and we
decided to design and release a new free framework that would allow anyone to
create a volunteer distributed EC experiment using cloud resources as
servers and browsers as clients.

%PABLO: He añadido el siguiente párrafo para el issue #31
There exist other volunteer frameworks written in compiled languages,
such as C++ or Java, that can achieve better performance than
JavaScript. However, one of the advantages of our system is that
clients do not need to install anything in their machines, they just
need to open a web page  
% Somewhat redundant 
% Javascript is the only language that can be executed in this way without any installation, 
% also removed the default, redundant with next sentence
in a compatible browser, such as Chrome, Safari or Firefox, which are
available in almost every desktop or mobile device. Other advantage is
that the source code can be directly examined by volunteers, because is not
compiled as other options (such as Java Applets, Flash scripts or
ActiveX). Also, as we discuss in this paper, it can provide some extra
features such as enhanced security or operating system independence.

%PABLO: hay que enlazar con el siguiente párrafo
Desktop clients have the same issues as any 
volunteer computing system, including our own: these issues are
related to security as well as
safety, which introduce a {\em social} aspect to the design of a
computing system that makes it a {\em techno-social system}
\cite{vespignani2009predicting}. In this paper our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page that runs the system
determine its performance and how it can be modeled and, eventually,
predicted.

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed
computation systems along with attempts to predict and model its behavior. 
Then, a detailed description of the proposed system is presented
in Section \ref{sec:description}, followed by the baseline experiments
in Section \ref{sec:experiments} and experiments using a new client
architecture that uses web workers in Section \ref{sec:w2}.
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

>>>>

\begin{abstract}
Volunteer computing is used routinely 
% (Paloma) Adverbs are always written before verbs, check this throughout the text
in science and industry, but it
still has a long way to go if it is going to become
% (Paloma) I would propose "a long way to go in order to become"
 a mainstream technology in
the same way the cloud technologies in general have. The lack of 
% (Paloma) Add "both" here to better complete the sentence
general
purpose and open source tools
with analytics built in
% (Paloma) "built-in" is an adjective and, as such, has to be written before names
 could be one of the reasons why this is so, as
well as the lack of proofs of concept. That is why in this paper we
present {\sf NodIO}, a framework used to create client-server architectures for distributed
evolutionary algorithms, written entirely % (Paloma) Adverb. I would also add an "and" after the comma
 in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser.  The architecture, along with some initial results on the
expected performance and scaling
behavior, is presented. We also use the algorithm data to
find out what kind of patterns the user behavior follow and try to fit
them to some statistical distribution.
\end{abstract}

@@

There is, then, space for systems that do not make any of these
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. {\sf NodIO} is first
% (Paloma) Is the "first" word really needed?
 a two tier client/server 
application, in which clients can run on a browser. 
Therefore, they can
% (Paloma) be embedded in?
 embedded any web-enabled device, including many over which 
the developers have no control.

Some time ago, our group faced the problem of diminishing funds for
buying new hardware. This was aggravated by the increasing maintenance costs and
extended downtime resulting from the continuous failures of existing
clusters.
Considering this, we leveraged 
% (Paloma) What 'something' did you leverage?
our experience in the design of web
applications, including JavaScript, since their inception and other
volunteer and
unconventional distributed evolutionary computing systems, and we
decided to design and release a new free framework that would allow anyone to
create a volunteer distributed EC experiment using cloud resources as
servers and browsers as clients.
% (Paloma) I think you should rewrite this whole sentence.
% For starters, focus in that you "leveraged" the problem through your deeply knowledge of... this and that. And "Thus/Then/Therefore", you decided...

%PABLO: He añadido el siguiente párrafo para el issue #31
There exist other volunteer frameworks written in compiled languages,
such as C++ or Java, that can achieve better performance than
JavaScript. However, one of the advantages of our system is that
clients do not need to install anything in their machines, they just
need to open a web page  
% Somewhat redundant 
% Javascript is the only language that can be executed in this way without any installation, 
% also removed the default, redundant with next sentence
in a compatible browser, such as Chrome, Safari or Firefox, which are
available in almost every desktop or mobile device. Other advantage is
that the source code can be directly examined by volunteers, because it is not
compiled as other options (such as Java Applets, Flash scripts or
ActiveX)
% (Paloma) Brackets not really needed here
. Also, as we discuss in this paper, it can provide some extra
features such as enhanced security or operating system independence.

%PABLO: hay que enlazar con el siguiente párrafo
Desktop clients have the same issues as any 
volunteer computing system, including our % (Paloma) their?
 own: these issues are
related to security as well as
safety, which introduce 
% (Paloma) Is the social aspect related to the word "safety"? It's not completely clear.
a {\em social} aspect to the design of a
computing system that makes it a {\em techno-social system}
\cite{vespignani2009predicting}. In this paper, our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page that runs the system
determine its performance and how it can be modeled and, eventually,
predicted.

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed
computation systems along with attempts to predict and model its behavior. 
Then, a detailed description of the proposed system is presented
in Section \ref{sec:description}, followed by the baseline experiments
in Section \ref{sec:experiments}, and experiments using a new client
architecture that uses web workers in Section \ref{sec:w2}.
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.
